---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# pkgInstaller

The goal of pkgInstaller is to be a stand alone space for some functions that are helpful when installing and managing packages.

One of the main functions, `install_missing_pkg`, borrows heavily from [INSTALLING MISSING PACKAGES FROM BIOCONDUCTOR, CRAN AND GITHUB](https://www.eokodie.com/blog/installing-missing-packages-from-bioconductor-cran-and-github/). This function requires that Bioconductor be installed. This package was created to get this function and dependency out of one of my other packages.

## Installation

You can install the development version of pkgInstaller with:

```{r, eval=FALSE}
devtools::install_github("emilelatour/pkgInstaller")
```

Make sure that [Bioconductor](https://bioconductor.org/install/) is installed.

```{r, eval=FALSE}
if (!requireNamespace("BiocManager"))
    install.packages("BiocManager")
BiocManager::install()
```

